
%Document generated using DScaffolding from https://www.mindmeister.com/1167676177
\documentclass{article}
\usepackage[utf8]{inputenc}

\newcommand{\todo}[1] {\iffalse #1 \fi} %Use \todo{} command for bringing ideas back to the mind map

\title{SLR data extraction}
\author{}

\begin{document}

\maketitle
      

\section{Introduction}

%Describe the practice in which the problem addressed appears
There is a growing body of literature that recognizes the importance of conducting secondary studies in Software Engineering (SE). Systematic Mapping Study (SM) and Systematic Literature Review (SLR) are the most common type of secondary studies conducted in SE. Main differences between SM and SLR are that the former aims to know what is done in a specific topic or area, or identify research gaps, whereas the latter aims to aggregate information from the outcomes of qualitative primary studies and reports a synthesis \cite{Kitchenham2015}, \cite{Wohlin2013}. Aggregation of papers resemble quantitative research, but a secondary study also includes a lot of judgment and coding of papers, which show large similarities with qualitative research \cite{Wohlin2013}.
%Most of the secondary studies are performed by novice researcher (e.g. phD students) \cite{Carver2013}. 
Conducting secondary studies in Software Engineering encompasses different activities: Protocol definition, Searching, Study Selection, Data extraction (DE), Data Synthesis and Reporting. As far as Data extraction (DE) is concerned, the extracted data feeds the next activity: classifying (in SM) and data synthesis (in SLR) \cite{Kitchenham2015}, \cite{Garousi2017}. 

Findings of any research should be as trustworthy as possible and every research study should be evaluated in relation to the methods used \cite{Cruzes2011}. Some knowledge of how the outcome was achieved is needed to trust the results. Mainly, the trustworthiness of a SLR will depend on the reliability of each different activities of conducting it. Cruzes et al. \cite{Cruzes2011} reported  that "The trustworthiness of a synthesis will depend on both the quality and the quantity of the evidence base it is built on". This also depends on the reliability of all the previous activities, i.e. Searching and Study selection, and Data Extraction.

Previous research acknowledges the importance of search strategy as a major contributor to the reliability of an SLR \cite{Ali2018}, \cite{Wohlin2013}, \cite{Kitchenham2012}, \cite{Macdonell2010}. However, Wohlin et al. reported in  \cite{Wohlin2013} that the outcomes can be influenced mainly by "the decisions taken by researchers and the judgements exercised" and by other factors, such as "the context of study, researchers conducting the study, and data available from the primary studies". Nowadays, the credibility of a research is done over what it is reported. The more description of method or process is reported, the more credible is a research. However, we think that the reported information (e.g. forms, number of extractor, whether peer reviewing is done) about the data extraction and synthesis is no sufficient or not reported in effective manner \cite{Budgen2018} in order to be the findings credible. Mainly, there is a lack of information about the rationales (e.g. evidence data in the primary study) that sustains the codes and themes presented in the synthesis. Besides, it is not common in SE to report the level of agreement in the classification, how many peer-reviewing meetings (or iteration) have been done, how many times and why a code has renamed or sorted in another theme. All this information will increase the credibility of a SLR findings,  give an opportunity to further research the SLR methodology in order to improve the guidelines, and be also useful to novices to learn about SLR methodology and SE topic.

Since evidences are gathered in the Data extraction activity, it is time to define what means "Reliability of Data Extraction".



\todo{What are the claims of SLR studies?} see \cite{Ali2018}, \cite{Kitchenham2013}
\todo{What are the benefits of SLR studies?}

    
    
%Describe the practical problem addressed, its significance and its causes
Research has shown that a major problem within conducting secondary studies in Software Engineering is that Secondary studies are not reported in a clear and effective manner \cite{Budgen2018}. Specifically, data extraction (including quality assessment), synthesis, and the process followed by reviewers need better reporting. This problem is of particular concern as it is now well established that it can affects negatively to the trustworthiness of the findings of the secondary study \cite{Cruzes2011}.

Credibility in thematic synthesis deals with extracting the most suitable units of data or segments of text, how well codes and themes cover data, or how to judge the similarities with and differences between themes.

This can lead to a SLR not be reliable \cite{Garousi2017}, \cite{Wohlin2013}, \cite{Kitchenham2011}, have little confidence on its findings, It is difficult to asses the scientific credibility of its results by SLR  readers and SLR results are difficult to compare. 

Causes can be diverse:
(1) the aggregations in codified form are hard to read and understand \cite{Dieste2008}
(2) lack of internal/external validation in order to mitigate researcher's bias\cite{Ampatzoglou2019}, 
(2) reviewers do not know which data is relevant \cite{Brereton2011}, (3) reviewers do not understand data extraction requirements \cite{Brereton2007} \cite{Zhou2017}, (4) innacurate or missing data: insufficient information for the extraction process \cite{Zhou2017}, (5) researcher is novice \cite{Ribeiro2018} \cite{Carver2013}, (6) relevant information is spread among different sections \cite{Budgen2018} \cite{Budgen2018}, (7) Extensive body of knowledge to be screened, classified and synthesized \cite{link.springer.com}, (8) effort to meet consensus (when many reviewers take part in data-extraction phase) \cite{Ribeiro2018} \cite{Riaz2010} \cite{Brereton2007} \cite{Staples2007} \cite{Bandara2015}, (9) too much time finding evidences, (10) too many studies to review \cite{Garousi2017}, (11) agenda problem and too many meetings \cite{Staples2007} \cite{Staples2007}, (12) geographically distributed-teams \cite{Riaz2010}, (13) researcher's bias \cite{Imtiaz2013} \cite{Ribeiro2018} \cite{Zhou2017} \cite{Ampatzoglou2019}, (14) data problems \cite{Bandara2015}, (15) data extraction forms are fulfilled manually or require too many mouse clicks \cite{Staples2007} \cite{Ramezani2017} \cite{Ramezani2017} \cite{Bandara2015} \cite{LU2008} and (16) Current specific software related to SLR and CAQDAS are not used. 
    
%Summarise existing research including knowledge gaps and give an account for similar and/or alternative solutions to the problem
Existing research has tackled these causes. Petersen et al. addressed the too much time finding evidences \cite{Petersen2015}. Garousi et al. addressed the too much time finding evidences \cite{Garousi2017}. However, this approach has the following limitation: they are fulfilled manually.

Garousi et al. addressed the geographically distributed-teams \cite{Garousi2017}. LU et al. addressed the data extraction forms are fulfilled manually or require too many mouse clicks \cite{LU2008}. Lu et al. addressed the data extraction forms are fulfilled manually or require too many mouse clicks \cite{Lu2008}. However, this approach has the following limitation: data format requirements \cite{Lu2008}. 
    
%Formulate goals and present Kernel theories used as a basis for the artefact design
In this work, we address 5 main causes: peer review is effort intensive and also takes more calendar time, too much time finding evidences, geographically distributed-teams, data problems and data extraction forms are fulfilled manually or require too many mouse clicks. To lessen these causes, we resort to provides a basis for establishing credibility and validity, make the examination of qualitative data more complete and rigorous, it is a requirement from the community, higher effectiveness, faciltate information sharing and knowledge exchange and interfaces to transfer data among tools. 
    
%Describe the kind of artefact that is developed or evaluated
This article presents a novel artefact
    
%Formulate research questions

    
%Summarize the contributions and their significance

      
%Overview of the research strategies and methods used
This article has followed a Design Science Research approach.

%Describe the structure of the paper
The remainder of the paper is structured as follows: 

%Optional - illustrate the relevance and significance of the problem with an example
    
      
\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
    